%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{lastpage}
\usepackage{trkchg}
\usepackage{engord}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Joseph James}{Radler}{ % Your name
\href{mailto:joseph.james.radler@gmail.com}{joseph.james.radler@gmail.com} | 765.412.4864 \\% Your contact information
2800 Franklin Ave E. \#17, Seattle WA, 98102 % Your website, LinkedIn profile or other web address
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------
\vspace{0pt}
\begin{minipage}[t]{0.32\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
%Contact &  Links
%------------------------------------------------
\section{Links} 
Github:// \href{https://github.com/jjradler}{\bf jjradler} \\
LinkedIn:// \href{https://www.linkedin.com/in/jjradler/}{\bf jjradler} \\
Webpage:// \href{http://jjradler.github.io}{\bf jjradler.github.io}

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 
\subsection{Univ. of Washington}
\descript{Master of Science (MS)}
\location{June 2018 | Seattle, WA}
Conc. in \textbf{Computational \& Theoretical Quantum Chemistry}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Purdue University}
\descript{Bachelor of Science (BS)}
\location{May 2012 | West Lafayette, IN}
Major in \textbf{Chemistry}\\
Minor in \textbf{Japanese Language}

\sectionspace

\subsection{Ivy Tech Comm. Coll.}
\descript{Associate of Applied Science (AAS)}
\location{Dec. 2010 | Lafayette, IN}
Major in \textbf{Chemical Technology}

%------------------------------------------------
% Skills 1
%------------------------------------------------

\section{Skills}
%\subsection{Quantitative}
%\textbf{Data:}	Analysis \textbullet{} Experiment Design\\
%Data Management \textbullet{} Statistics\\
%Time-Frequency Analysis \textbullet{} Visualization\\
%\textbf{Mathematics:}	Discrete Mathematics\\
%Group Theory \textbullet{} Linear Algebra\\
%Numerical Analysis \textbullet{} Vector Calculus

%------------------------------------------------
% Communicaiton
%------------------------------------------------
\subsection{Communication}
Technical Writing \textbullet{} Editing\\
Visualizations \textbullet{} Developing Tutorials\\
Publishing \textbullet{} Website Construction\\
Lecturing \textbullet{} Mentoring \textbullet{} Training\\
Poster \& Oral Presentation

\sectionspace

\subsection{Computing}
Automation \textbullet{} Development\\
Distributed \& High-Performance Computing \textbullet{} Package Managers\\
Scientific Computing \textbullet{} Scripting

\sectionspace

\subsection{Programming}
\textbf{Proficient:}	Bash \textbullet{} MATLAB \textbullet{} LaTeX\\
Markdown \textbullet{} Python 2.7 \& 3.x\\
\textbf{Familiar:}	C$/$C++ \textbullet{} HTML
% \textbf{Learning:}	Haskell \textbullet{} Javascript \textbullet{} Scala

\sectionspace

\subsection{Software Tools:}
\textbf{Packages:}	MATLAB\textbullet{} Git \textbullet{} Mathematica\\
\textbf{Workload Schedulers:}	 PBS \textbullet{} Slurm\\
\textbf{IDEs:}		IntelliJ \textbullet{} PyCharm \textbullet{} Vim

\sectionspace

%------------------------------------------------
% Languages
%------------------------------------------------
\subsection{Natural Languages}
%\sectionspace
\textbf{Native or Fluent:}	English\textbullet{}Japanese\\
\textbf{Proficient:}	French\textbullet{}German\textbullet{}Portuguese\\
Russian\textbullet{}Spanish\\
\textbf{Limited:}		Korean\textbullet{}Mandarin


%\subsection{Operating Systems}
%\textbf{Proficient:}		Windows \textbullet{} MacOS\\
%\textbf{Familiar:}	Linux (Fedora \& Ubuntu)\\


\end{minipage} % The end of the left column
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\vspace{0pt}
\begin{minipage}[t]{0.65\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Research
%------------------------------------------------

\section{Work \& Research Experience}
\subsection{University of Washington | Seattle, WA}
\descript{Graduate Teaching Assistant / Associate | General Chemistry\\
Department of Chemistry}
\location{Sept. 2015 - Mar. 2019}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Trained undergraduate students with no prior chemistry background in laboratory safety and procedures, as well as theoretical and technical aspects of chemistry.
\item Conveyed abstract concepts from physics in the context of introductory-level chemistry courses.
\item Drafted and published examination and study questions.
\item Led and advised other Graduate Teaching Assistants as a Mentor Teaching Assistant.
\item Served as instructor for a First Year Graduate student Teaching Assistant Orientation seminar.
\end{tightitemize}
\sectionspace 

\descript{Research Assistant | Xiaosong Li Group\\
Department of Chemistry}
\location{Jan 2016 - Sept. 2018}
\begin{tightitemize}
\item Collaborated with several research groups from various experimental disciplines. 
\item Developed strategies, calculation pipelines, data analysis tools, and simulation software modules. 
\item Wrote, edited, and created visualizations for a national research center grant application
\item Troubleshot complicated, interlocked assemblies of software, theoretical models, and data analysis techniques.
\item Built automation pipelines for simulations, analysis, and data management.
\item Analyzed large, complex data sets generated from complex simulations.
\item Reported data as tables and visualizations.
\item Presented proposals, methods, analyses, and conclusions in both small-group settings and public seminars.
\item Wrote and published collaborative articles in peer-reviewed journals.
\end{tightitemize}
\sectionspace % Some whitespace after the section

\subsection{Purdue Rare Isotope Measurement (PRIME) Laboratory}
\descript{Chemist | Geological Sample Processing Chemistry Operations}
\location{May 2012 - Aug 2015 | West Lafayette, IN}
\begin{tightitemize}
\item Processed soil, rock, and water samples for \textsuperscript{36}Cl analysis by Accelerator Mass Spectrometry.
\item Optimized sample processing, tripling sample throughput.
\item Re-engineered document workflows and maintained records for the database.
\item Revised safety protocols for the handling of hydrofluoric acid (HF) and other hazardous reagents.
\item Wrote and revised sample processing documentation and procedures.
\item Brought hazardous waste handling and disposal into compliance.
\item Instructed visiting scholars from around the globe in processing techniques
\item Collaborated remotely with researchers to advise them with their own processing facilities.
\item Trained undergraduate and graduate students in laboratory techniques and safety.
\end{tightitemize}
\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

\newpage % Start a new page

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Joseph James}{Radler}{ % Your name
\href{mailto:joseph.james.radler@gmail.com}{joseph.james.radler@gmail.com} | 765.412.4864 \\% Your contact information
2800 Franklin Ave E. \#17, Seattle WA, 98102 % Physical Address
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------
\vspace{0pt}
\begin{minipage}[t]{0.32\textwidth} % The left column takes up 33% of the text width of the page
%------------------------------------------------
% Professional Skills
%------------------------------------------------
\section{Skills}
\sectionspace
%%------------------------------------------------
%% Communicaiton
%%------------------------------------------------
%\subsection{Communication}
%\sectionspace
%Laboratory Instruction \textbullet{} Lecturing\\
%Mentoring \textbullet{} Safety Training\\
%Developing \& Delivering Tutorials\\
%Poster \& Oral Presentation\\
%Technical Writing \textbullet{} Editing\\
%Publishing \textbullet{} Website Construction 

\subsection{Quantitative}
\sectionspace
\textbf{Data:}\\
Analysis \textbullet{} Experiment Design\\
Data Management \textbullet{} Statistics\\
Time-Frequency Analysis \textbullet{} Visualization\\

\textbf{Mathematics:}\\
Discrete Mathematics\\
Group Theory \textbullet{} Linear Algebra\\
Numerical Analysis \textbullet{} Vector Calculus

\sectionspace\sectionspace

\subsection{Collaboration}
\sectionspace
Intellectually Curious \textbullet{} Adaptable\\
Self-Motivated \textbullet{} Fast Learner\\
Flexible \textbullet{} Diplomatic \textbullet{} Articulate

\sectionspace
%%------------------------------------------------
%% Languages
%%------------------------------------------------
%\subsection{Natural Languages}
%\sectionspace
%\textbf{Native or Fluent:}\\English\textbullet{}Japanese\\
%\textbf{Proficient:}\\French\textbullet{}German\textbullet{}Portuguese\\
%Russian\textbullet{}Spanish\\
%\textbf{Limited:}\\Korean\textbullet{}Mandarin


\sectionspace

\subsection{Operating Systems}
\sectionspace
\textbf{Proficient:}		Windows \textbullet{} MacOS\\
\textbf{Familiar:}	Linux (Fedora \& Ubuntu)
\sectionspace
%------------------------------------------------
% Coursework
%------------------------------------------------
\section{Relevant Courses}

\subsection{Writing and Language}
\sectionspace
\textbullet{}Grant and Proposal Writing\\
\textbullet{}Technical Writing and Editing\\
\textbullet{}English Composition\\
\textbullet{}Japanese Language \& Literature

\sectionspace

\subsection{Computer Programming}
\sectionspace
\textbullet{}High-Performance Computing\\
\textbullet{}C Programming\\
\textbullet{}Intro Engineering with MATLAB\\
\textbullet{}Developing Quantum Models

\sectionspace

\subsection{Mathematics}
\sectionspace
\textbullet{}Numerical Linear Algebra\\
\textbullet{}Computational Data Analysis\\
\textbullet{}Ordinary Differential Equations\\
\textbullet{}Multivariable \& Vector Calculus
\sectionspace

\subsection{Chemistry}
\sectionspace
\textbullet{}Advanced Inorganic Chemistry\\
\textbullet{}Computational Chemistry\\
\textbullet{}Intro. Quantum Chemistry\\
\textbullet{}Quantum Chemistry

\end{minipage} % The end of the left column%
%\hfill
\vspace{0pt}
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.65\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
%  Publications
%------------------------------------------------
\section{Publications}
\begin{itemize}
\item \textbf{Radler, J. J.}; Lingerfelt, D. B.; Castellano, F. N.; Chen, L. X.; Li, X.;	\textit{Role of Vibrational Dynamics on Excited-State Electronic Coherence in a Binuclear Platinum Complex} (Featured Cover Article) J. Phys. Chem. A, \textbf{2018}. \href{https://pubs.acs.org/doi/10.1021/acs.jpca.8b01352}{\textit{DOI:} 10.1021/acs.jpca.8b01352}

\item Lingerfelt, D. B.; Lestrange, P. J.; \textbf{Radler, J. J.}; Brown-Xu, S. E.; Kim, P.; Castellano, F. N.; Chen, L. X.; Li, X.;	\textit{Can Excited State Electronic Coherence Be Tuned via Molecular Structural Modification? A First-Principles Quantum Electronic Dynamics Study of Pyrazolate-Bridged Pt(II) Dimers}.
J. Phys. Chem. A., \textbf{2017}. \href{https://pubs.acs.org/doi/10.1021/acs.jpca.6b12099}{\textit{DOI:} 10.1021/acs.jpca.6b12099}
\end{itemize}

%------------------------------------------------
% Presentations
%------------------------------------------------
\section{Poster Presentations}
\begin{itemize}
\item \textbf{Radler, J. J.}; Lingerfelt, D. B.; Li, X.; \emph{Cascading into Coherence -- Theoretical Investigations of Long-Lived Excited State Coherences in Bimetallic Pt(II) Complexes}. Conference on Excited State Processes (ESP 2018);	\textbf{\textit{06/2018}}.

\item \textbf{Radler, J. J.}; Lingerfelt, D. B.; Li, X.; \emph{Exploring the Role of Nuclear Motion on Excited State Coherences in Binuclear Pyrazolate-Bridged Platinum Complexes}. 1st Northwest Theoretical and Computational Chemistry Conference;	\textbf{\textit{10/2017}}.

\item Houferak, C.; Kasper, J.; \textbf{Radler, J. J.}; Sun, S.; \emph{Applications of Compressive Sensing to Simulated Chemical Spectra}. University of Washington Engineering in Data Science Symposium;	\textbf{\textit{03/2016}}

\item \textbf{Radler, J. J.}; Jackson, G. S.; Koopman, H.; Westgate, A.; \emph{Determination of \textsuperscript{14}C Pelagic Ocean Values through Atomic Bomb Radiocarbon Dating of Dolphin Teeth}. 13\textsuperscript{th} Accelerator Mass Spectrometry Conference;	\textbf{\textit{08/2014}}.

\item \textbf{Radler, J. J.}; Schauer, D. J.; \emph{Probing the Nature of Metal-Phosphonate Interactions by FTIR Spectroscopy}, Central Regional Meeting of the ACS;	\textbf{\textit{06/2010}}.
\end{itemize}

%------------------------------------------------
%  CERTIFICATIONS
%------------------------------------------------

\section{Certifications}
\textbf{IBM Data Science Professional Certificate Issued by Coursera}
\begin{tightitemize}
\item \textbf{Apr. 2019:} \href{https://www.coursera.org/account/accomplishments/certificate/WWSD2GBMB8EX}{\textit{Databases and SQL for Data Science}}
\item \textbf{Apr. 2019:} \href{https://www.coursera.org/account/accomplishments/certificate/W4EADFQY28ZJ}{\textit{Python for Data Science}}
\item \textbf{Mar. 2019:} \href{https://www.coursera.org/account/accomplishments/certificate/5BM3VZET3N9E}{\textit{Data Science Methodology}}
\item \textbf{Feb. 2019:} \href{https://www.coursera.org/account/accomplishments/certificate/A2LTPE84WG4H}{\textit{Open Source Tools for Data Science}}
\item \textbf{Feb. 2019:} \href{https://www.coursera.org/account/accomplishments/certificate/MLKNRE5BPR9X}{\textit{What is Data Science?}}
\end{tightitemize}
%------------------------------------------------
% Awards
%------------------------------------------------
\section{Awards} 
\sectionspace
\begin{tightitemize}
\item \href{https://www.newswise.com/doescience/?article_id=684936&returnurl=aHR0cHM6Ly93d3cubmV3c3dpc2UuY29tL2FydGljbGVzL2xpc3Q=}{\textbf{2017} J. Phys. Chem. A Award for Best Original Research Poster (1\textsuperscript{st} NWTCC) }
\item \textbf{2012} Dean's List, Purdue University
\item \textbf{2010} Dean's List, Graduated with Honors, Ivy Tech Community College
\end{tightitemize}

%------------------------------------------------
% Societies
%------------------------------------------------
\section{Societies} 
\sectionspace
\begin{tightitemize}
\item \textbf{2017} University of Washington Chemistry Graduate Student Mentor Network
\item \textbf{2016} Society of Industrial and Applied Mathematicians (SIAM)
\item \textbf{2016} UW High-Performance Computing Club (UW-HPCC)
\item \textbf{2015} American Chemical Society (ACS)
\item \textbf{2006} Alpha Chi Sigma Beta Nu Chapter
\end{tightitemize}
\end{minipage} % The end of the right column
%----------------------------------------------------------------------------------------

\end{document}